Ethnicity sensitive author disambiguation of semi-labeled corpora of scientific articles

### 2015-08-24 paper/paper.tex
save

% future improvements

\glnote{Mention Hussein's thesis for further experiments}
\glnote{Virtuous circle}

>>>>

In this work, we have revisited and validated the general author disambiguation
pipeline introduced in previous and independent research works. The generic
approach is made of three components, whose design and tuning are all critical
to get good performance: (i) a blocking function for pre-clustering signatures
and reducing computational complexity, (ii) a linkage function for identifying
signatures with corefering authors and (iii) the agglomerative clustering of
signatures. Making use of a distinctively large dataset of more than 1 million
crowdsourced annotations, we experimentally study all three components and
propose further improvements. With regards to blocking, we suggest to use
phonetization of author names to increase recall while maintaining low
computational complexity. For the linkage function, we introduce
ethnicity-sensitive features for the automatic tailoring of disambiguation to non-Western
author names whenever necessary. Finally, we explore semi-supervised cut-off
threshold strategies for agglomerative clustering. For all three components,
experiments show that our refinements all yield significantly better author
disambiguation accuracy, thereby encouraging further research in these directions.

As part of this study, we also publicly release the annotated data extracted
from the INSPIRE platform, and on which our experiments are based on. To the
best of our knowledge, data of this size and coverage is the first to be
available in  author disambiguation research. By releasing the data publicly,
we hope to set a benchmark on which further research on author disambiguation
and related topics can  build upon.

\section*{Acknowledgements}

\glnote{todo}
